---
title: "Salvage shortcomings? Comparing the geographic and taxonomic representation between salvaged and actively collected museum specimens in the state of California."
author: "Samantha L. Rutledge^1^ ^2^*"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: template/doc_prefix.tex
      in_header: template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2:
    toc: no
    reference_docx: template/nature_style.docx
    number_sections: no
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: ref.bib
always_allow_html: yes
links-as-notes: true
notes-after-punctuation: false
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
options(digits = 3, width = 88,
        # use pdf file automatically when compile to pdf
        knitr.graphics.auto_pdf = TRUE, 
        knitr.kable.NA = '')

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/preamble.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/doc_prefix.tex'
tpl_3 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/nature_style.docx'
# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
# change directory accordingly
if(!file.exists(tpl_1f <- 'template/preamble.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- 'template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
if(!file.exists(tpl_3f <- 'template/nature_style.docx')) download.file(tpl_3, tpl_3f)

if(knitr::is_latex_output() | knitr::is_html_output()){
  library(kableExtra)
} else {
  options(kableExtra.auto_format = FALSE) # for docx
}
```

\footnotesize 

^1^Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA  
^2^Museum of Natural Science, Louisiana State University, Baton Rouge, LA, USA

\* **Corresponding author**, email: daijianglee@gmail.com; 125 Life Science Building, Baton Rouge, LA 70803

\normalsize

**Running headline**: Environment and species richness

**Abstract**: Your awesome abstract here.

\clearpage

# Introduction

Natural history collections are vital sources of primary biological material, being utilized in a variety of studies across evolutionary biology, pathology, and ecotoxicology, among other disciplines (Lister et al. 2011, McClean et al. 2016, Rutledge & Barve in press ). Providing insight into temporal and spatial trends across species GIVE EXAMPLES, collections are vital for understanding how species and populations change over time, patterns that lay the foundation for conservation practices (Winker et al. 1991, Pyke & Ehrlich 2010, Rutledge & Barve in press). GIVE EXAMPLES OF CONSERVATION POLICIES. 

Here is your introduction. It should describe clearly the rationale for the study being done and the previous work related with the study. It should also tell readers about your specific hypothese/questions being addressed. Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993; @williamson_dissolved_1999]

However, to maintain such records of past and present of biological diversity, constant addition to collections is necessary. EXPLAIN WHY IN MORE DETAIL. Normally done via active collecting, current specimen collection has decreased noticeably in the past few decades, with many museums abstaining from this practice altogether (Sweet 2010, Schultz et al. 2021). Fueling this decrease is a simultaneous increase in public and professional resistance to collecting birds for research purposes, resistance that in turn hampers attempts by museums to obtain collecting permits (Sweet 2010). NAME WHY THIS IS UNFOUNDED CONCERN.  Consequently, many museums have turned to other methods of acquiring new specimens, including salvage. 

Salvaged specimens, broadly defined as any specimen that was not intentionally killed for placement within a museum collection (Sweet 2010), come in many forms, including victims of roadkill, euthanizations at wildlife hospitals, and building collisions, among others (Sweet 2010). Yet, salvaged specimens are likely an inadequate replacement for active collecting. Many salvaged specimens arrive to the museum in poor condition (limiting the amount of information, such as intact tissue samples and complete skeletons, that can be obtained) and/or without any geolocating information (key for any study requiring information on the specimen’s geographic context when collected) (Sweet 2010). Further, unintentional taxonomic and geographic biases may be introduced. Most salvaged specimens are gathered from areas that are open and easily accessible to humans (Sweet 2010). Areas and habitats that are harder to access (e.g., areas away from roads, rivers, etc.) may thus be underrepresented in collections. Further, many species falling victim to primary salvage sources, such as building collisions, are primarily migrants, potentially leading to an overrepresentation of such species in collections and an underrepresentation of more sedentary species and populations (Schultz et al. 2021). 

Despite these concerns, no study has assessed the geographic or taxonomic extent covered by salvaged specimens. Here, I propose to conduct a case study on Californian birds within the collection of University of California (UC) Berkley’s Museum of Vertebrate Zoology, assessing the geographic and taxonomic coverage of salvaged versus actively collected museum specimens.

# Methods

##Data 
All data was obtained from the Arctos database (GIVE SOURCE), for all bird specimens collected within the last 20 years in the state of California that are currently housed at the Museum of Vertebrate Zoology, UC Berkley. Data was cleaned, wrangled, visualized, and analyzed in R (NAME VERSION) (see below). Both raw and final datasets are available from github repository (NAME REPOSITORY, PROVIDE LINK). See below for R workflow.

##R Workflow: Reading, Cleaning, Wrangling, Visualizing Data
```{r}
### load appropriate libraries
library(tidyverse)
library(readr)
```

```{r}
### Import dataset
Arctos_birds_Calif_2000_2020 <- read_csv("final_project/Data/Arctos_birds_Calif_2000_2020.csv")
```

```{r}
### Identify unknown/blank collecting methods ###
Arctos_birds_Calif_2000_2020$coll_method_2 <- ifelse(is.na(Arctos_birds_Calif_2000_2020$collecting_method), "unknown","known")
```

```{r}
### Assign specimen entries as 'salvaged' if collecting method is unknown and specimen locality is an address ###
Arctos1 <- Arctos_birds_Calif_2000_2020 %>% mutate(coll_method_4 = ifelse(coll_method_2 == "unknown" & grepl("^[0-9]+", spec_locality, ignore.case = T) & !grepl(" mi | km | block | m | yds ", spec_locality, ignore.case = T), "salvage", "unknown"))

### Assign specimen entries as 'salvaged' if collecting method is unknown and parts is just a 'skull' and/or specimen locality is a highway###
Arctos2 <- Arctos1 %>% mutate(coll_method_3 = ifelse(coll_method_2 == "unknown" & is.na(collectors), "salvage", ifelse(coll_method_2 == "unknown" & parts %in% c(grep("^skull\\w*", parts, value=T)), "salvage", ifelse(coll_method_2 == "unknown" & spec_locality %in% c(grep("highway|hwy", spec_locality, ignore.case = T, value = T)),"salvage", ifelse(coll_method_4 == "salvage", "salvage", "unknown")))))
```

Here is the method section. You can include equations easily. For inline equations, use $\text{var}(X) = p(1-p)$. For display equation, use

$$\text{var}(X) = p(1-p)$$

## Results


#### Tables

Insert tables by `kable` in knitr package in R. Then cross-reference it back with: see Table \@ref(tab:tableName).

(ref:captionTable1) **Model coefficients of leaf senescence based on in situ data**. No space at the end of this line!!

```{r tableName,results='asis',echo=FALSE, message=F, warning=F}
source("R/rcode.R")
# linesep = c('', '', '', '', '', '\\addlinespace') 
# can be used within kable to specify linespace
knitr::kable(sprich, booktabs = T, caption = '(ref:captionTable1)')  %>%
 kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "condensed", "hover"), 
                           latex_options = c("striped", "HOLD_position")) # , "scale_down"
```

Put results inline, e.g. the mean species richness is `r meansprich`.

#### Insert tables by `xtable` package in R


Show as Table. \ref{t:anova}:

```{r echo=F,results='asis',warning=F,message=F}
library(xtable)
envi.summ = xtable(summary(envi.aov),label = "t:anova", caption = "Caption here")
print(envi.summ,
		caption.placement = "top",
	  floating=T,
	  hline.after=NULL,
	  comment = FALSE,
	  add.to.row=list(pos=list(-1,0, nrow(envi.summ)),
	  command=c(
		   '\\toprule\n',
		  '\\midrule\n',
		   '\\bottomrule\n')))
```

#### Insert tables by hand


Show as Table. \@ref(tab:byhand):

Table: (#tab:byhand) Caption here.

Col A             Col B       Col C                   Col D
------------      -------     ------------------      ------------------
row 1             190         $112 \pm 2$             $233 \pm 3$
$\eta$            0.13        0.12                    0.12
$\eta^2$          0.14        0.13                    0.50
$\eta^3$          0.15        0.31                    0.52


#### Figures

Insert figure by code chunk. And cross-ref it back as Figure \@ref(fig:figName).

(ref:captionFig1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figName, fig.width=7, fig.asp=1, fig.cap="(ref:captionFig1)"}
ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
  geom_point() + geom_smooth(method = "lm") +
  facet_wrap(~envi, scales = "free_x") + 
  theme_bw()
```


Or if you already have the figure: 

And cite it as Figure \@ref(fig:fig2).

(ref:captionFig2) **No - or _ in the caption ref.** No space at the end of this line!

```{r fig2, out.width='70%', fig.cap="(ref:captionFig2)"}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```

More details can be found at [here](https://bookdown.org/yihui/bookdown/).

# References

<div id="refs"></div>

\clearpage

\setcounter{page}{0}
\pagenumbering{arabic}
\setcounter{page}{1}


\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand {\thetable}{S\arabic{table}}
\renewcommand {\thefigure}{S\arabic{figure}}


# Supporting Information

## Figures

(ref:captionFigS1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figS1, out.width='70%', fig.cap="(ref:captionFigS1)"}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```
