---
title: "Salvage shortcomings? Comparing the geographic and taxonomic representation between salvaged and actively collected museum specimens in the state of California."
author: "Samantha L. Rutledge^1^ ^2^*"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: template/doc_prefix.tex
      in_header: template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2:
    toc: no
    reference_docx: template/nature_style.docx
    number_sections: no
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: ref.bib
always_allow_html: yes
links-as-notes: true
notes-after-punctuation: false
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
options(digits = 3, width = 88,
        # use pdf file automatically when compile to pdf
        knitr.graphics.auto_pdf = TRUE, 
        knitr.kable.NA = '')

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/preamble.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/doc_prefix.tex'
tpl_3 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/nature_style.docx'
# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
# change directory accordingly
if(!file.exists(tpl_1f <- 'template/preamble.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- 'template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
if(!file.exists(tpl_3f <- 'template/nature_style.docx')) download.file(tpl_3, tpl_3f)

if(knitr::is_latex_output() | knitr::is_html_output()){
  library(kableExtra)
} else {
  options(kableExtra.auto_format = FALSE) # for docx
}
```

\footnotesize 

^1^Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA  
^2^Museum of Natural Science, Louisiana State University, Baton Rouge, LA, USA

\* **Corresponding author**, email: daijianglee@gmail.com; 125 Life Science Building, Baton Rouge, LA 70803

\normalsize

**Running headline**: Environment and species richness

**Abstract**: Your awesome abstract here.

\clearpage

# Introduction

Acting as repositories of the Earth's past and present biodiversity, natural history collections are vital sources of primary biological material. Preserving records of temporal and spatial trends in said biodiversity, collections have been (and continue to be) employed in a variety of studies across evolutionary biology, pathology, and ecotoxicology, among other disciplines (Lister et al. 2011, McClean et al. 2016, Rutledge & Barve in press ). Further, collections are vital for understanding how species and populations change over time, patterns that lay the foundation for conservation practices (Winker et al. 1991, Pyke & Ehrlich 2010, Rutledge & Barve in press). GIVE EXAMPLES OF CONSERVATION POLICIES. 

Here is your introduction. It should describe clearly the rationale for the study being done and the previous work related with the study. It should also tell readers about your specific hypothese/questions being addressed. Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993; @williamson_dissolved_1999]

However, to maintain such records of past and present of biological diversity, constant addition to collections is necessary. Without constant addidtions, the time series of specimens - essential to documenting trends (see above) - would be interuppted, limiting the collection's usefulness to present and future generations of researchers. Unfortunately, with many museums abstaining from this practice altogether (Sweet 2010, Schultz et al. 2021). This is primarily due to the growing public - and even professional resistance - to traditional active collecting (i.e., intentionally killing birds with the intent of placement in a natural history collection). Though for the most part based on misinformation and a lack of knowledge on the importance and impact of collecting (CITE), such resistance has nevertheless hampered attempts by museums to obtain collecting permits (Sweet 2010). NAME WHY THIS IS UNFOUNDED CONCERN.  Consequently, many museums have turned to other methods of acquiring new specimens, including salvage. 

Salvaged specimens, broadly defined as any specimen that was not intentionally killed for placement within a museum collection (Sweet 2010), come in many forms, including victims of roadkill, euthanizations at wildlife hospitals, and building collisions, among others (Sweet 2010). Yet, salvaged specimens are likely an inadequate replacement for active collecting. Many salvaged specimens arrive to the museum in poor condition (limiting the amount of information, such as intact tissue samples and complete skeletons, that can be obtained) and/or without any geographic information (key for any study requiring information on the specimen’s geographic context when collected) (Sweet 2010). Further, unintentional taxonomic and geographic biases may be introduced. Most salvaged specimens are gathered from areas that are open and easily accessible to humans (Sweet 2010). Areas and habitats that are harder to access (e.g., areas away from roads, rivers, etc.) may thus be underrepresented in collections. Further, many species falling victim to primary salvage sources, such as building collisions, are primarily migrants, potentially leading to an overrepresentation of such species in collections and an underrepresentation of more sedentary species and populations (Schultz et al. 2021). 

Despite these concerns, no study has assessed the geographic or taxonomic extent covered by salvaged specimens. Here, I  conduct a case study on Californian birds within the collection of University of California (UC) Berkley’s Museum of Vertebrate Zoology, assessing the geographic (county) and taxonomic (genera) coverage of salvaged versus actively collected museum specimens.

# Methods

##Data 
All data was obtained from the Arctos database (GIVE SOURCE), for all bird specimens collected within the last 20 years in the state of California that are currently housed at the Museum of Vertebrate Zoology, UC Berkley. Data was cleaned, wrangled, visualized, and analyzed in R (NAME VERSION) (see below). Both raw and final datasets are available from github repository (NAME REPOSITORY, PROVIDE LINK). See below for R workflow.

##R Workflow: Reading, Cleaning, Wrangling, Visualizing Data
```{r}
### load appropriate libraries
library(tidyverse)
library(readr)
```

```{r}
### Import dataset
Arctos_birds_Calif_2000_2020 <- read_csv("final_project/Data/Arctos_birds_Calif_2000_2020.csv")
```

```{r}
### Identify unknown/blank collecting methods ###
Arctos_birds_Calif_2000_2020$coll_method_2 <- ifelse(is.na(Arctos_birds_Calif_2000_2020$collecting_method), "unknown","known")
```

```{r}
### Assign specimen entries as 'salvaged' if collecting method is unknown and specimen locality is an address ###
Arctos1 <- Arctos_birds_Calif_2000_2020 %>% mutate(coll_method_4 = ifelse(coll_method_2 == "unknown" & grepl("^[0-9]+", spec_locality, ignore.case = T) & !grepl(" mi | km | block | m | yds ", spec_locality, ignore.case = T), "salvage", "unknown"))

### Assign specimen entries as 'salvaged' if collecting method is unknown and parts is just a 'skull' and/or specimen locality is a highway###
Arctos2 <- Arctos1 %>% mutate(coll_method_3 = ifelse(coll_method_2 == "unknown" & is.na(collectors), "salvage", ifelse(coll_method_2 == "unknown" & parts %in% c(grep("^skull\\w*", parts, value=T)), "salvage", ifelse(coll_method_2 == "unknown" & spec_locality %in% c(grep("highway|hwy", spec_locality, ignore.case = T, value = T)),"salvage", ifelse(coll_method_4 == "salvage", "salvage", "unknown")))))
```

```{r}
### Remove entries w/ 'parts' that are just eggs, nests, or blood ###
df <- Arctos2 %>% filter(!(parts=="egg" | parts  =="egg; nest" | parts == "nest; egg" | parts == "media; egg"))
df2 <- df %>% filter(!(parts=="blood" | parts  =="blood; blood" | parts == "blood; blood; blood" | parts == "blood; blood; blood; blood"))
```

```{r}
### remove entries with 'parts' that are 'unknown' or 'nest', as well as 'age' embryo or chick
df3 <- df2 %>% filter(!(parts=="nest" | parts  =="unknown"))
df4 <- df3 %>% filter(!(age == "embryo" | age == "chick" | age == "downy chick" | age == "downy chick, completely covered in fuzz, eyes still closed" | age == "naked chick, eyes closed" | age == "downy chick, fuzz on body, eyes not open" | age == "downy chick, pre-fledge" | age == "downy fledgling" | age == "not yet fully fledged, still downy" | age == "skull unossified, downy (only slightly fuzzy on head & backside of the body" | age == "skull unossified, naked & downy (some fuzz on head and backside, eyes still closed)" | age == "skull unossified, transitioning from naked to downy, eyes closed" | age == "skull unossified, downy, eyes closed" | age == "skull unossified, between naked and downy (some fuzz on head and backside, eyes still closed)")) 
```

```{r}

### Assign entries as 'salvage' if parts are just tissue/tissue sample/wing
df41 <- df4 %>% mutate(coll_method_5 = ifelse(df4$parts=="tissue" | df4$parts == "tissue; tissue sample" | df4$parts == "wing; tissue", "salvage", "unknown"))
```

```{r}
### assign as 'salvage' based on specimen locality ####
df51 <- df41 %>% 
    mutate(coll_method_6 = ifelse(spec_locality == "Aviary in Oakland" | spec_locality == "aviary of Monica J. Albe, Oakland" | spec_locality == "San Diego Zoo" | spec_locality == "CAPTIVE, San Diego Zoo [probably]" | spec_locality == "CAPTIVE, San Diego Zoo" | spec_locality == "San Francisco Zoo, San Francisco" | spec_locality == "Zoological Society of San Diego" | spec_locality == "Zoological Society of San Diego, CAPTIVE" | spec_locality == "CAPTIVE Zoological Societ of San Diego" | spec_locality == "CAPTIVE Zoological Society of San Diego" | spec_locality == " San Diego: Sea World CAPTIVE" | spec_locality == "Amador High School, 1155 Santa Rita Rd., Pleasanton" | spec_locality == "Pittsburg High School, Pittsburg" | spec_locality == "no specific locality recorded" | spec_locality == "unknown" | spec_locality == "Life Sciences Building courtyard, University of California campus, Berkeley" | spec_locality == "Natural Resources Building, Mineral" | spec_locality == "Outside Earth and Marine Sciences Building, University of California, Santa Cruz" | spec_locality == "near south door of Valley Life Sciences Building, University of California campus, Berkeley" | spec_locality == "near Protein Design Labs (34801 Campus Drive), near Dumbarton Bridge, Fremont" | spec_locality == "W side of Dwinelle Hall, Univ. Calif. campus, Berkeley" | spec_locality == "in vicinity of breezeway between Birge and LeConte Halls, University of California campus, Berkeley" | spec_locality == "Stadium Rim Way between Centennial Rd. and Galey Rd., University of California campus, Berkeley" | spec_locality == "University of California campus, Berkeley" | spec_locality == "University of California Riverside campus, Riverside" | spec_locality == "north side of Hildebrand Hall, University of California campus, Berkeley" | spec_locality == "east side of Lewis Hall, University of California Berkeley campus" |spec_locality == "Unit 2 Dormitory, between Channing and Haste Streets, Berkeley" | spec_locality == "Strawberry Creek Lodge (1320 Addison Street), Berkeley" | spec_locality == "Davis" | spec_locality == "University of California Botanical Garden, Strawberry Canyon, Berkeley" | spec_locality == "Berkeley" | spec_locality == "Life Sciences Addition, University of California, Berkeley" | spec_locality == "Donner Lab, University of California, Berkeley" | spec_locality == "California Hall, University of California, Berkeley" | spec_locality == "Women's Faculty Club, University of California, Berkeley" | spec_locality == "Linsdale Library, Hastings Natural History Reservation" | spec_locality == "San Rafael, 24 Madrona Street" | spec_locality == "San Diego: Sea World CAPTIVE" | spec_locality == "Edwards AFB" | spec_locality == "classroom at Hastings Natural History Reservation" | spec_locality == "labs at Hastings Natural History Reservation, Carmel Valley" | spec_locality == "Lawrence Livermore National Lab" | spec_locality == "outside the Davis Lab, Hastings Natural History Reservation, Carmel Valley" | spec_locality == "Sacramento" | spec_locality == "El Cerrito" | spec_locality == "Ojai" | spec_locality == "Livermore" | spec_locality == "Inverness" | spec_locality == "Bolinas" | spec_locality == "Oakland" | spec_locality == "Pittsburg" | spec_locality == "Pleasant Valley" | spec_locality == "Bethel Island" | spec_locality == "Woodacre" | spec_locality == "Jamesburg" | spec_locality == "Nicasio" | spec_locality == "La Casa de Maria, 801 Ladera Lane, Santa Barbara" | spec_locality == "Anaheim" | spec_locality == "Pt. Mugu Naval Base, Air National Guard hanger" | spec_locality == "Carmel Valley" | spec_locality == "Hopland Research and Extension Center bunkhouse" | spec_locality == "Wildlife Gallery, Bolinas" | spec_locality == "Alameda Naval Station, Alameda" | spec_locality == "Mills College, Oakland", "salvage", "unknown"))
```

```{r}
### reassign NAs as '0' to prevent 'NA' output in new column ###
df6 <- df51 %>% mutate(coll_NAs = ifelse(is.na(collecting_method), "unknown", "known"))
df6$collecting_method[is.na(df6$collecting_method)] <- 0

### Assign entries with known 'collecting method' as 'salvage' or 'active'
df7 <- df6 %>% 
    mutate(coll_method_7 = ifelse(collecting_method == "dead on road" | collecting_method == "died on barbed wire fence" | collecting_method == "euthanized" | collecting_method == "euthanized while at Wetlands and Wildlife Care Center" | collecting_method == "euthanized while at WWCC" | collecting_method == "found injured and transferred to WWCC where euthanized" | collecting_method == "found injured, transferred to WWCC and euthanized" | collecting_method == "found injured, transferred to WWCC where euthanized" | collecting_method == "found injured, transferred to WWCC, 'wobbly, lies down often', and euthanized on 2019-08-11" | collecting_method == "gift" | collecting_method == "salavage" | collecting_method == "salbage" | collecting_method == "salvage (caught in Tomahawk trap)" | collecting_method == "salvage" | collecting_method == "salvage (mammal trap)" | collecting_method == "salvaged" | collecting_method == "salvage-hit by vehicle", "salvage", ifelse(collecting_method == "feeder trap" | collecting_method == "feeder trap and observational" | collecting_method == "funnel trap" | collecting_method == "mistnet" | collecting_method == "mistnet and observational" | collecting_method == "netted" | collecting_method == "rat trap" | collecting_method == "shot" | collecting_method == "shotgun" | collecting_method == "trap" | collecting_method == "trapped with bow net", "active","unknown")))

### Now build another column, lumping together all coll_methods and assigning as active or salvage
df8 <- df7 %>% mutate(coll_method = ifelse(coll_method_2 == "unknown" & coll_method_3 == "salvage", "salvage", ifelse(coll_method_2 == "unknown" & coll_method_4 == "salvage", "salvage", ifelse(coll_method_2 == "unknown" & coll_method_5 == "salvage","salvage", ifelse(coll_method_2 == "unknown" & coll_method_6 == "salvage", "salvage", ifelse(coll_method_7 == "salvage", "salvage", ifelse(coll_method_7 == "active", "active", "active")))))))


```

```{r}
### make column for genus
library(stringi)
df8$genus <- stri_extract_first_regex(df8$scientific_name, "\\S+")
```

```{r}
### split data frame in two: active dataset and salvage dataset

df_salvage <- df8[which(df8$coll_method == "salvage"),]
df_active <- df8[which(df8$coll_method == "active"),]
```

```{r}
### Calculate count, proportions/percentages for salvaged and actively collected specimens for county and genera ###

salvage_data_genus <- df_salvage %>%
  group_by(genus) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

salvage_data_county <- df_salvage %>%
  group_by(county) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

active_data_genus <- df_active %>%
  group_by(genus) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

active_data_county <- df_active %>%
  group_by(county) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

```

```{r}
### get top counties and genera for salvage and active datasets

salvage_descend_county <- salvage_data_county[order(-salvage_data_county$cnt),]

salvage_descend_genus <- salvage_data_genus[order(-salvage_data_genus$cnt),]

active_descend_county <- active_data_county[order(-active_data_county$cnt),]

active_descend_genus <- active_data_genus[order(-active_data_genus$cnt),]
```

```{r}
### merge datasets together to see how they compare by genus
salvage_active_dataset_genus <-merge(salvage_data_genus, active_data_genus, by.x = "genus", by.y = "genus", all.x = TRUE)

```

```{r}
### merge datasets together to see how they compare by county
salvage_active_dataset_county <-merge(salvage_data_county, active_data_county, by.x = "county", by.y = "county", all.x = TRUE)

```

```{r}
### now for scatterplots
p1 <- ggplot(salvage_active_dataset_genus, aes(x=genus, y=cnt.y)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_1 <- p1 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")
plot_1
```


```{r}
### more scatterplots
p2 <- ggplot(salvage_active_dataset_genus, aes(x=genus, y=cnt.x)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_2 <- p2 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")
plot_2
```


```{r}
### combine scatterplots
p <- ggplot() +
      # blue plot
      geom_point(data=salvage_active_dataset_genus, aes(x=genus, y=cnt.x),color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2) +
      # red plot
      geom_point(data=salvage_active_dataset_genus, aes(x=genus, y=cnt.y), color = "grey33", fill ="red",shape = 21, alpha = 0.5, size = 2, stroke = 2 )+ theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")



```

```{r}
### as above, but scatterplots for county now
p3 <- ggplot(salvage_active_dataset_county, aes(x=county, y=cnt.y)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_3 <- p3 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")
plot_3

p4<- ggplot(salvage_active_dataset_county, aes(x=county, y=cnt.x)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_4 <- p4 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")
plot_4
```

```{r}
### now combine scatterplots
q <- ggplot() +
      # blue plot
      geom_point(data=salvage_active_dataset_county, aes(x=county, y=cnt.x),color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2) +
      # red plot
      geom_point(data=salvage_active_dataset_county, aes(x=county, y=cnt.y), color = "grey33", fill ="red",shape = 21, alpha = 0.5, size = 2, stroke = 2 )+ theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")

```

##R Workflow: Data Analysis

Two Chi Squares Goodness of Fit were conducted, one to determine whether the genera represented by salvaged specimens was statistically different from those represented by actively collected specimens, a second to compare the same for county representation. The percentages calculated for actively collected and salvaged specimens were inputted as expected and observed values, respectively.

```{r}
### now time for chi squares, using active percentages (calculated above) as expected values, to compare genera representation
observed <- salvage_active_dataset_genus$freq.x
expected <- salvage_active_dataset_genus$freq.y

chisq.test(observed, expected)
```

```{r}
### now time for chi squares, using active percentages (calculated above) as expected values, to compare county representation
observed <- salvage_active_dataset_county$freq.x
expected <- salvage_active_dataset_county$freq.y

chisq.test(observed, expected)
```

## Results

Salvaged (n = NAME NUMBER) and actively collected (n = NAME NUMBER) specimens represented NAME PROPORTION and NAME PROPORTION of the specimens contained within the final dataset. For genera: NAME NUMBERS were represented, respectively (Figure 1). For county: NAME NUMBERS were represented (Figure 2). See Table 1 and Table 2 for genera and county counts, respectively, for salvaged and actively collected specimens. Chi squares were significant for both genera (LIST VALUES) and county (LIST VALUES), with salvaged specimens having significantly different proportions represented for genera and county than actively collected specimens. 

#### Figures

Insert figure by code chunk. And cross-ref it back as Figure \@ref(fig:figName).

(ref:captionFig1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figName, fig.width=7, fig.asp=1, fig.cap="(ref:captionFig1)"}
ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
  geom_point() + geom_smooth(method = "lm") +
  facet_wrap(~envi, scales = "free_x") + 
  theme_bw()
```



#### Tables

Insert tables by `kable` in knitr package in R. Then cross-reference it back with: see Table \@ref(tab:tableName).

(ref:captionTable1) **Model coefficients of leaf senescence based on in situ data**. No space at the end of this line!!

```{r tableName,results='asis',echo=FALSE, message=F, warning=F}
source("R/rcode.R")
# linesep = c('', '', '', '', '', '\\addlinespace') 
# can be used within kable to specify linespace
knitr::kable(sprich, booktabs = T, caption = '(ref:captionTable1)')  %>%
 kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "condensed", "hover"), 
                           latex_options = c("striped", "HOLD_position")) # , "scale_down"
```

Put results inline, e.g. the mean species richness is `r meansprich`.

#### Insert tables by `xtable` package in R


Show as Table. \ref{t:anova}:

```{r echo=F,results='asis',warning=F,message=F}
library(xtable)
envi.summ = xtable(summary(envi.aov),label = "t:anova", caption = "Caption here")
print(envi.summ,
		caption.placement = "top",
	  floating=T,
	  hline.after=NULL,
	  comment = FALSE,
	  add.to.row=list(pos=list(-1,0, nrow(envi.summ)),
	  command=c(
		   '\\toprule\n',
		  '\\midrule\n',
		   '\\bottomrule\n')))
```

#### Insert tables by hand


Show as Table. \@ref(tab:byhand):

Table: (#tab:byhand) Caption here.

Col A             Col B       Col C                   Col D
------------      -------     ------------------      ------------------
row 1             190         $112 \pm 2$             $233 \pm 3$
$\eta$            0.13        0.12                    0.12
$\eta^2$          0.14        0.13                    0.50
$\eta^3$          0.15        0.31                    0.52


#### Figures

Insert figure by code chunk. And cross-ref it back as Figure \@ref(fig:figName).

(ref:captionFig1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figName, fig.width=7, fig.asp=1, fig.cap="(ref:captionFig1)"}
ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
  geom_point() + geom_smooth(method = "lm") +
  facet_wrap(~envi, scales = "free_x") + 
  theme_bw()
```


Or if you already have the figure: 

And cite it as Figure \@ref(fig:fig2).

(ref:captionFig2) **No - or _ in the caption ref.** No space at the end of this line!

```{r fig2, out.width='70%', fig.cap="(ref:captionFig2)"}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```

More details can be found at [here](https://bookdown.org/yihui/bookdown/).

# Discussion



# References

<div id="refs"></div>

\clearpage

\setcounter{page}{0}
\pagenumbering{arabic}
\setcounter{page}{1}


\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand {\thetable}{S\arabic{table}}
\renewcommand {\thefigure}{S\arabic{figure}}


# Supporting Information

## Figures

(ref:captionFigS1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figS1, out.width='70%', fig.cap="(ref:captionFigS1)"}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```
