---
title: "Salvage shortcomings? Comparing the geographic and taxonomic representation between salvaged and actively collected museum specimens in the state of California."
author: "Samantha L. Rutledge^1^ ^2^*"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: template/doc_prefix.tex
      in_header: template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2:
    toc: no
    reference_docx: template/nature_style.docx
    number_sections: no
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: ref.bib
always_allow_html: yes
links-as-notes: true
notes-after-punctuation: false
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
options(digits = 3, width = 88,
        # use pdf file automatically when compile to pdf
        knitr.graphics.auto_pdf = TRUE, 
        knitr.kable.NA = '')

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/dlilab/manuscript_template/master/Doc/template/preamble.tex'
tpl_2 = 'https://raw.githubusercontent.com/dlilab/manuscript_template/master/Doc/template/doc_prefix.tex'
tpl_3 = 'https://raw.githubusercontent.com/dlilab/manuscript_template/master/Doc/template/nature_style.docx'
# bib_1 = 'https://raw.githubusercontent.com/dlilab/manuscript_template/master/template/ref.bib'
# change directory accordingly
if(!file.exists(tpl_1f <- 'template/preamble.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- 'template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
if(!file.exists(tpl_3f <- 'template/nature_style.docx')) download.file(tpl_3, tpl_3f)

if(knitr::is_latex_output() | knitr::is_html_output()){
  library(kableExtra)
} else {
  options(kableExtra.auto_format = FALSE) # for docx
}
```

\footnotesize 

^1^Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA  
^2^Museum of Natural Science, Louisiana State University, Baton Rouge, LA, USA

\* **Corresponding author**, email: srutle6@lsu.edu; Museum of Natural Science, Baton Rouge, LA 70803

\normalsize

**Running headline**: Salvaged vs collected specimens

\clearpage

# Introduction

Acting as repositories of the Earth's past and present biodiversity, natural history collections are vital sources of primary biological material [@winker2010importance]. Preserving records of temporal and spatial trends in said biodiversity, collections have been (and continue to be) employed in a variety of studies across evolutionary biology, pathology, and ecotoxicology, among other disciplines [@winker2010importance]. Further, collections are vital for understanding how species and populations change over time, patterns that lay the foundation for conservation practices [@gotelli2021estimating, @schmitt2019museum]. 

However, to maintain such records of past and present of biological diversity, constant addition to collections is necessary. Without constant additions, the time series of specimens - essential to documenting trends (see above) - would be interrupted, limiting the collection's usefulness to present and future generations of researchers [@hromada2015old]. Unfortunately, with many museums abstaining from this practice altogether [@sweet2010collection]. This is primarily due to the growing public - and even professional resistance - to traditional active collecting (i.e., intentionally killing birds with the intent of placement in a natural history collection)[@greenfieldboyce_is_2014, @russo2017collection] . Though for the most part based on misinformation and a lack of knowledge on the importance and impact of collecting, such resistance has nevertheless hampered attempts by museums to obtain collecting permits [@sweet2010collection]. Consequently, many museums have turned to other methods of acquiring new specimens, including salvage. 

Salvaged specimens, broadly defined as any specimen that was not intentionally killed for placement within a museum collection [@sweet2010collection], come in many forms, including victims of roadkill, euthanizations at wildlife hospitals, and building collisions, among others [@sweet2010collection]. Yet, salvaged specimens are likely an inadequate replacement for active collecting. Many salvaged specimens arrive to the museum in poor condition (limiting the amount of information, such as intact tissue samples and complete skeletons, that can be obtained) and/or without any geographic information (key for any study requiring information on the specimen’s geographic context when collected) [@sweet2010collection]. Further, unintentional taxonomic and geographic biases may be introduced. Most salvaged specimens are gathered from areas that are open and easily accessible to humans [@sweet2010collection]. Areas and habitats that are harder to access (e.g., areas away from roads, rivers, etc.) may thus be underrepresented in collections [@boakes2010distorted, @dias2018informative]. Further, many species falling victim to primary salvage sources, such as building collisions, are primarily migrants, potentially leading to an overrepresentation of such species in collections and an underrepresentation of more sedentary species and populations [@shultz2021natural]. 

Despite these concerns, no study has assessed the geographic or taxonomic extent covered by salvaged specimens. Here, I  conduct a case study on Californian birds within the collection of University of California (UC) Berkley’s Museum of Vertebrate Zoology, assessing the geographic (county) and taxonomic (genera) coverage of salvaged versus actively collected museum specimens.

# Methods

## Data

All data was obtained from the Arctos database (GIVE SOURCE), for all bird specimens collected within the last 20 years in the state of California that are currently housed at the Museum of Vertebrate Zoology, UC Berkley. Data was cleaned, wrangled, visualized, and analyzed in R (4.0.2) (see below). Both raw and final datasets are available from github repository (https://github.com/slrutledge27/BIOL7800). See below for R workflow.

##R Workflow: Reading, Cleaning, Wrangling, Visualizing Data
```{r}
### load appropriate libraries
library(tidyverse)
library(readr)
```

```{r}
### Import dataset
Arctos_birds_Calif_2000_2020 <- read_csv("Data/Arctos_birds_Calif_2000_2020.csv")
```

```{r}
### Identify unknown/blank collecting methods ###
Arctos_birds_Calif_2000_2020$coll_method_2 <- ifelse(is.na(Arctos_birds_Calif_2000_2020$collecting_method), "unknown","known")
```

```{r}
### Assign specimen entries as 'salvaged' if collecting method is unknown and specimen locality is an address ###
Arctos1 <- Arctos_birds_Calif_2000_2020 %>% mutate(coll_method_4 = ifelse(coll_method_2 == "unknown" & grepl("^[0-9]+", spec_locality, ignore.case = T) & !grepl(" mi | km | block | m | yds ", spec_locality, ignore.case = T), "salvage", "unknown"))

### Assign specimen entries as 'salvaged' if collecting method is unknown and parts is just a 'skull' and/or specimen locality is a highway###
Arctos2 <- Arctos1 %>% mutate(coll_method_3 = ifelse(coll_method_2 == "unknown" & is.na(collectors), "salvage", ifelse(coll_method_2 == "unknown" & parts %in% c(grep("^skull\\w*", parts, value=T)), "salvage", ifelse(coll_method_2 == "unknown" & spec_locality %in% c(grep("highway|hwy", spec_locality, ignore.case = T, value = T)),"salvage", ifelse(coll_method_4 == "salvage", "salvage", "unknown")))))
```

```{r}
### Remove entries w/ 'parts' that are just eggs, nests, or blood ###
df <- Arctos2 %>% filter(!(parts=="egg" | parts  =="egg; nest" | parts == "nest; egg" | parts == "media; egg"))
df2 <- df %>% filter(!(parts=="blood" | parts  =="blood; blood" | parts == "blood; blood; blood" | parts == "blood; blood; blood; blood"))
```

```{r}
### remove entries with 'parts' that are 'unknown' or 'nest', as well as 'age' embryo or chick
df3 <- df2 %>% filter(!(parts=="nest" | parts  =="unknown"))
df4 <- df3 %>% filter(!(age == "embryo" | age == "chick" | age == "downy chick" | age == "downy chick, completely covered in fuzz, eyes still closed" | age == "naked chick, eyes closed" | age == "downy chick, fuzz on body, eyes not open" | age == "downy chick, pre-fledge" | age == "downy fledgling" | age == "not yet fully fledged, still downy" | age == "skull unossified, downy (only slightly fuzzy on head & backside of the body" | age == "skull unossified, naked & downy (some fuzz on head and backside, eyes still closed)" | age == "skull unossified, transitioning from naked to downy, eyes closed" | age == "skull unossified, downy, eyes closed" | age == "skull unossified, between naked and downy (some fuzz on head and backside, eyes still closed)")) 
```

```{r}

### Assign entries as 'salvage' if parts are just tissue/tissue sample/wing
df41 <- df4 %>% mutate(coll_method_5 = ifelse(df4$parts=="tissue" | df4$parts == "tissue; tissue sample" | df4$parts == "wing; tissue", "salvage", "unknown"))
```

```{r}
### assign as 'salvage' based on specimen locality ####
df51 <- df41 %>% 
    mutate(coll_method_6 = ifelse(spec_locality == "Aviary in Oakland" | spec_locality == "aviary of Monica J. Albe, Oakland" | spec_locality == "San Diego Zoo" | spec_locality == "CAPTIVE, San Diego Zoo [probably]" | spec_locality == "CAPTIVE, San Diego Zoo" | spec_locality == "San Francisco Zoo, San Francisco" | spec_locality == "Zoological Society of San Diego" | spec_locality == "Zoological Society of San Diego, CAPTIVE" | spec_locality == "CAPTIVE Zoological Societ of San Diego" | spec_locality == "CAPTIVE Zoological Society of San Diego" | spec_locality == " San Diego: Sea World CAPTIVE" | spec_locality == "Amador High School, 1155 Santa Rita Rd., Pleasanton" | spec_locality == "Pittsburg High School, Pittsburg" | spec_locality == "no specific locality recorded" | spec_locality == "unknown" | spec_locality == "Life Sciences Building courtyard, University of California campus, Berkeley" | spec_locality == "Natural Resources Building, Mineral" | spec_locality == "Outside Earth and Marine Sciences Building, University of California, Santa Cruz" | spec_locality == "near south door of Valley Life Sciences Building, University of California campus, Berkeley" | spec_locality == "near Protein Design Labs (34801 Campus Drive), near Dumbarton Bridge, Fremont" | spec_locality == "W side of Dwinelle Hall, Univ. Calif. campus, Berkeley" | spec_locality == "in vicinity of breezeway between Birge and LeConte Halls, University of California campus, Berkeley" | spec_locality == "Stadium Rim Way between Centennial Rd. and Galey Rd., University of California campus, Berkeley" | spec_locality == "University of California campus, Berkeley" | spec_locality == "University of California Riverside campus, Riverside" | spec_locality == "north side of Hildebrand Hall, University of California campus, Berkeley" | spec_locality == "east side of Lewis Hall, University of California Berkeley campus" |spec_locality == "Unit 2 Dormitory, between Channing and Haste Streets, Berkeley" | spec_locality == "Strawberry Creek Lodge (1320 Addison Street), Berkeley" | spec_locality == "Davis" | spec_locality == "University of California Botanical Garden, Strawberry Canyon, Berkeley" | spec_locality == "Berkeley" | spec_locality == "Life Sciences Addition, University of California, Berkeley" | spec_locality == "Donner Lab, University of California, Berkeley" | spec_locality == "California Hall, University of California, Berkeley" | spec_locality == "Women's Faculty Club, University of California, Berkeley" | spec_locality == "Linsdale Library, Hastings Natural History Reservation" | spec_locality == "San Rafael, 24 Madrona Street" | spec_locality == "San Diego: Sea World CAPTIVE" | spec_locality == "Edwards AFB" | spec_locality == "classroom at Hastings Natural History Reservation" | spec_locality == "labs at Hastings Natural History Reservation, Carmel Valley" | spec_locality == "Lawrence Livermore National Lab" | spec_locality == "outside the Davis Lab, Hastings Natural History Reservation, Carmel Valley" | spec_locality == "Sacramento" | spec_locality == "El Cerrito" | spec_locality == "Ojai" | spec_locality == "Livermore" | spec_locality == "Inverness" | spec_locality == "Bolinas" | spec_locality == "Oakland" | spec_locality == "Pittsburg" | spec_locality == "Pleasant Valley" | spec_locality == "Bethel Island" | spec_locality == "Woodacre" | spec_locality == "Jamesburg" | spec_locality == "Nicasio" | spec_locality == "La Casa de Maria, 801 Ladera Lane, Santa Barbara" | spec_locality == "Anaheim" | spec_locality == "Pt. Mugu Naval Base, Air National Guard hanger" | spec_locality == "Carmel Valley" | spec_locality == "Hopland Research and Extension Center bunkhouse" | spec_locality == "Wildlife Gallery, Bolinas" | spec_locality == "Alameda Naval Station, Alameda" | spec_locality == "Mills College, Oakland", "salvage", "unknown"))
```

```{r}
### reassign NAs as '0' to prevent 'NA' output in new column ###
df6 <- df51 %>% mutate(coll_NAs = ifelse(is.na(collecting_method), "unknown", "known"))
df6$collecting_method[is.na(df6$collecting_method)] <- 0

### Assign entries with known 'collecting method' as 'salvage' or 'active'
df7 <- df6 %>% 
    mutate(coll_method_7 = ifelse(collecting_method == "dead on road" | collecting_method == "died on barbed wire fence" | collecting_method == "euthanized" | collecting_method == "euthanized while at Wetlands and Wildlife Care Center" | collecting_method == "euthanized while at WWCC" | collecting_method == "found injured and transferred to WWCC where euthanized" | collecting_method == "found injured, transferred to WWCC and euthanized" | collecting_method == "found injured, transferred to WWCC where euthanized" | collecting_method == "found injured, transferred to WWCC, 'wobbly, lies down often', and euthanized on 2019-08-11" | collecting_method == "gift" | collecting_method == "salavage" | collecting_method == "salbage" | collecting_method == "salvage (caught in Tomahawk trap)" | collecting_method == "salvage" | collecting_method == "salvage (mammal trap)" | collecting_method == "salvaged" | collecting_method == "salvage-hit by vehicle", "salvage", ifelse(collecting_method == "feeder trap" | collecting_method == "feeder trap and observational" | collecting_method == "funnel trap" | collecting_method == "mistnet" | collecting_method == "mistnet and observational" | collecting_method == "netted" | collecting_method == "rat trap" | collecting_method == "shot" | collecting_method == "shotgun" | collecting_method == "trap" | collecting_method == "trapped with bow net", "active","unknown")))

### Now build another column, lumping together all coll_methods and assigning as active or salvage
df8 <- df7 %>% mutate(coll_method = ifelse(coll_method_2 == "unknown" & coll_method_3 == "salvage", "salvage", ifelse(coll_method_2 == "unknown" & coll_method_4 == "salvage", "salvage", ifelse(coll_method_2 == "unknown" & coll_method_5 == "salvage","salvage", ifelse(coll_method_2 == "unknown" & coll_method_6 == "salvage", "salvage", ifelse(coll_method_7 == "salvage", "salvage", ifelse(coll_method_7 == "active", "active", "active")))))))


```

```{r}
### make column for genus
library(stringi)
df8$genus <- stri_extract_first_regex(df8$scientific_name, "\\S+")
```

```{r}
### split data frame in two: active dataset and salvage dataset

df_salvage <- df8[which(df8$coll_method == "salvage"),]
df_active <- df8[which(df8$coll_method == "active"),]
```

```{r}
### Calculate count, proportions/percentages for salvaged and actively collected specimens for county and genera ###

salvage_data_genus <- df_salvage %>%
  group_by(genus) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

salvage_data_county <- df_salvage %>%
  group_by(county) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

active_data_genus <- df_active %>%
  group_by(genus) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

active_data_county <- df_active %>%
  group_by(county) %>%
  summarise(cnt = n()) %>%
  mutate(freq = round(cnt / sum(cnt), 3))

```

```{r}
### get top counties and genera for salvage and active datasets

salvage_descend_county <- salvage_data_county[order(-salvage_data_county$cnt),]

salvage_descend_genus <- salvage_data_genus[order(-salvage_data_genus$cnt),]

active_descend_county <- active_data_county[order(-active_data_county$cnt),]

active_descend_genus <- active_data_genus[order(-active_data_genus$cnt),]
```

```{r}
### merge datasets together to see how they compare by genus
salvage_active_dataset_genus <-merge(salvage_data_genus, active_data_genus, by.x = "genus", by.y = "genus", all.x = TRUE)

```

```{r}
### merge datasets together to see how they compare by county
salvage_active_dataset_county <-merge(salvage_data_county, active_data_county, by.x = "county", by.y = "county", all.x = TRUE)

```

```{r}
### now for scatterplots for genera
p1 <- ggplot(salvage_active_dataset_genus, aes(x=genus, y=cnt.y)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_1 <- p1 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")
plot_1
```


```{r}
### more scatterplots, for genera
p2 <- ggplot(salvage_active_dataset_genus, aes(x=genus, y=cnt.x)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_2 <- p2 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")
plot_2
```


```{r}
### combine scatterplots, both salvaged and actively collected genera
p <- ggplot() +
      # blue plot
      geom_point(data=salvage_active_dataset_genus, aes(x=genus, y=cnt.x),color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2) +
      # red plot
      geom_point(data=salvage_active_dataset_genus, aes(x=genus, y=cnt.y), color = "grey33", fill ="red",shape = 21, alpha = 0.5, size = 2, stroke = 2 )+ theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")



```

```{r}
### as above, but scatterplots for county now
p3 <- ggplot(salvage_active_dataset_county, aes(x=county, y=cnt.y)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_3 <- p3 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")
plot_3

p4<- ggplot(salvage_active_dataset_county, aes(x=county, y=cnt.x)) + geom_point(color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2)

plot_4 <- p4 + theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")
plot_4
```

```{r}
### now combine scatterplots for county
q <- ggplot() +
      # blue plot
      geom_point(data=salvage_active_dataset_county, aes(x=county, y=cnt.x),color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2) +
      # red plot
      geom_point(data=salvage_active_dataset_county, aes(x=county, y=cnt.y), color = "grey33", fill ="red",shape = 21, alpha = 0.5, size = 2, stroke = 2 )+ theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")

```

## R Workflow: Data Analysis

Two Chi Squares Goodness of Fit were conducted, one to determine whether the genera represented by salvaged specimens was statistically different from those represented by actively collected specimens, a second to compare the same for county representation. The percentages calculated for actively collected and salvaged specimens were inputted as expected and observed values, respectively.

```{r}
### now time for chi squares, using active percentages (calculated above) as expected values, to compare genera representation
observed <- salvage_active_dataset_genus$freq.x
expected <- salvage_active_dataset_genus$freq.y

chisq.test(observed, expected)
```

```{r}
### now time for chi squares, using active percentages (calculated above) as expected values, to compare county representation
observed <- salvage_active_dataset_county$freq.x
expected <- salvage_active_dataset_county$freq.y

chisq.test(observed, expected)
```

## Results

Salvaged and actively collected specimens represented the following proportions of specimens contained within the final dataset:

```{r}
Table1 = as.table(table(df8$coll_method))
prop.table(Table1)
```

For genera: 171 and 137 were represented for salvaged and actively collected specimens, respectively \@ref(fig:Figure1). For county: 56 and 53 were represented \@ref(fig:Figure2) for salvaged and actively collected specimens, respectively. See \@ref(tab:Table2) and \@ref(tab:Table3) for genera and county counts, respectively, for salvaged and actively collected specimens. Chi squares were significant for both genera:

```{r}
### now time for chi squares, using active percentages (calculated above) as expected values, to compare genera representation
observed <- salvage_active_dataset_genus$freq.x
expected <- salvage_active_dataset_genus$freq.y

chisq.test(observed, expected)
```

and county:

```{r}
### now time for chi squares, using active percentages (calculated above) as expected values, to compare county representation
observed <- salvage_active_dataset_county$freq.x
expected <- salvage_active_dataset_county$freq.y

chisq.test(observed, expected)
```
 
 ,with salvaged specimens having significantly different proportions represented for genera and county than actively collected specimens. 

#### Figures

(ref:Figure1cap) **Genera represented by salvaged (blue dots) and actively collected (red dots) specimens**.

```{r Figure1, fig.width=7, fig.asp=1, fig.cap="(ref:Figure1cap)"}
### scatterplot for genera
ggplot() +
      # blue plot
      geom_point(data=salvage_active_dataset_genus, aes(x=genus, y=cnt.x),color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2) +
      # red plot
      geom_point(data=salvage_active_dataset_genus, aes(x=genus, y=cnt.y), color = "grey33", fill ="red",shape = 21, alpha = 0.5, size = 2, stroke = 2 )+ theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "Genus", y = "Number of Specimens")
```

(ref:Figure2cap) **Counties represented by salvaged (blue dots) and actively collected (red dots) specimens**

```{r Figure2, fig.width=7, fig.asp=1, fig.cap="(ref:Figure2cap)"}
### scatterplot for county

ggplot() +
      # blue plot
      geom_point(data=salvage_active_dataset_county, aes(x=county, y=cnt.x),color = "grey33", fill = "darkturquoise", shape = 21, alpha = 0.5, size = 2, stroke = 2) +
      # red plot
      geom_point(data=salvage_active_dataset_county, aes(x=county, y=cnt.y), color = "grey33", fill ="red",shape = 21, alpha = 0.5, size = 2, stroke = 2 )+ theme(legend.position = "none",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), panel.grid = element_blank()) + labs(x = "County", y = "Number of Specimens")
```


#### Tables

```{r}
Table1 = as.table(table(df8$coll_method))
prop.table(Table1)
```

```{r Table2, eval=FALSE}
knitr::kable(salvage_descend_genus[1:171,1:2], col.names = c("Genus", "Specimen Count"), caption = "Table 2.1: The total number of salvaged specimens representing each genera", format="markdown")

knitr::kable(active_descend_genus[1:171,1:2], col.names = c("Genus", "Specimen Count"), caption = "Table 2.2: The total number of actively collected specimens representing each genera", format="markdown")

```

```{r Table3, eval=FALSE}
knitr::kable(salvage_descend_county[1:171,1:2], col.names = c("County", "Specimen Count"), caption = "Table 3.1: The total number of salvaged specimens representing each county", format="markdown")

knitr::kable(active_descend_county[1:171,1:2], col.names = c("County", "Specimen Count"), caption = "Table 3.2: The total number of actively collected specimens representing each county", format="markdown")
```


# Discussion
`
The taxonomic and geographic representation of avian specimens housed within the Museum of Vertebrate Zoology was significantly different between salvage and actively collected specimens. Thus, as speculated, the taxonomic and geographic representation provided by salvaged versus actively collected specimens are not the same. However, salvaged specimens unexpectedly had greater representation in more counties and genera than actively collected specimens, though several counties and genera represented by salvaged specimens were not represented by active collecting (and vice versa). 

Taxonomic coverage for salvaged specimens was surprisingly greater for salvage than actively collected specimens; however, this finding is likely due the inclusion of specimens sourced from Californian zoos, aviaries, and other captive populations. Such sources often contain species that are non-local to the area (i.e., exotic) [@sweet2010collection]. 

Geographic coverage was also lower for actively collected than salvaged specimens. One reason for this may be the difficulty involved in obtaining permits to actively collect versus salvage: due to public/professional resistance towards active collecting, it may be harder – or even impossible – to obtain permission to obtain birds in certain areas through traditional collecting methods (e.g., shotgun, mistnet) [@minteer2014avoiding, @remsen1995importance . Further, for salvaged specimens, the top five counties where specimens were obtained are within the top 20 most populated in California; as such, such locales are likely more developed, with more structures increasing the risk of collision deaths/window strikes in birds, leading to greater opportunities for salvage [@klem2014landscape, @rioux2013avian ,  . Meanwhile, top counties for active collection are among the least populated in California; additionally, they are underrepresented by salvaged specimens (i.e., many counties in which actively collected specimens are obtained contain no or few salvaged samples). This again may reflect the difficulty of obtaining salvaged specimens from locales that are less frequented (and therefore less likely for a dead bird to be found before it is scavenged), as well as less developed (resulting in fewer deaths by collision, leading to a dependence on actively collected specimens to represent these regions) [@klem2014landscape, @rioux2013avian].

While insightful, this comparison of salvage and active collected specimens remains very coarse. For instance, regarding geographic coverage, it would be interesting to see which specific localities within counties salvaged versus actively collected specimens are being collected; it is likely that biases may appear, with specific areas having a higher number of citizens involved in salvaging specimens. Additionally, as mentioned above, salvaged specimens are more likely to be sourced from around a few highly developed areas, while actively collected specimens may show a more general distribution (potentially providing a more accurate idea of presence/absence data of species within the county). An examination of each county based on its population and/or level of structural development would be insightful for ascertaining any geographic biases associated with salvaged specimens, a crucial step for accounting for said biases in future studies [@dias2018informative]. Finally, future comparisons should account for specimens obtained from aviary/zoos when calculating taxonomic representation, to ascertain whether salvaged specimens do in fact represent a greater taxonomic coverage than actively collected specimens, or whether such representation is artificially inflated by the inclusion of exotic taxa. 

# Conclusion

Salvaged and actively collected specimens provide different pictures of the biodiversity within the state of California, for both taxonomy (genus level) and geography (county level). As such, adding to natural history collections through salvage will not replace actively collecting specimens, nor can actively collected specimens be expected to encompass the representation provided by salvaged records. Consequently, both salvage and active collecting are needed for the most comprehensive representation of avian biodiversity in museum collections.

# References

<div id="refs"></div>

\clearpage

\setcounter{page}{0}
\pagenumbering{arabic}
\setcounter{page}{1}


\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand {\thetable}{S\arabic{table}}
\renewcommand {\thefigure}{S\arabic{figure}}
