---
title: "hw_06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
##data
x = c(110.5, 105.4, 118.1, 104.5, 93.6, 84.1, 77.8, 75.6)
y = c(5.755, 5.939, 6.010, 6.545, 6.730, 6.750, 6.899, 7.862)
```

##1 The data consist of a predictor variable x, plant height, and a response variable y, grain yield, for eight varieties of rice.
##  Consider fitting a simple linear regression model y_i = \beta_0 + \beta_1x_i+\varepsilon_iy 

### a.
```{r}
get_coeff <- lm(y~x)
get_coeff
```
Answer: ^B1 = -0.03717; ^B1 is the slope of the best fit line, determining the EXPECTED change in y as x changes

###b

```{r}
summary(get_coeff)
```
```{r}
anova(get_coeff)
```


Answer: Both t and F-statistic are significant, indicating that this regression model is a good fit for the data at hand

### c.

```{r}
qt(0.05/2, 6,lower.tail = FALSE)
```
```{r}
summary(get_coeff)$coefficients
```



```{r}
confint(get_coeff, level = 0.95)

```


### d.

```{r}
par(mfrow = c(2, 2))
plot(get_coeff)
```

### e. 

Answer: estimated standard error for residuals obtained from summary table above = 0.3624, with 6 degrees of freedom

### f. 

```{r}

predict(get_coeff, newdata = data.frame(x = 100), interval = "confidence")
```

### g.
```{r}
predict(get_coeff, newdata = data.frame(x = 100), interval = "prediction")
```


### h.
```{r}
summary(get_coeff)$r.squared
```

##2.

```{r}
d <- data.frame(x = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
y = c(-2.08, -0.72, 0.28, 0.92, 1.20, 1.12, 0.68, -0.12, -1.28))
```

### a. 
```{r}
plot(d$x, d$y)
```

### b.

```{r}

d_lm_model = lm(y ~ x, data=d)
d_lm_model
d_resid = resid(d_lm_model)
plot(d$y, d_resid)
plot(d$x, d_resid)
plot(fitted(d_lm_model ), d_resid)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


Answer: 