---
title: "hw_04"
author: "Samantha Rutledge"
date: "10/26/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
tinytex::install_tinytex()
```



## 1.  Use the rvest R package to scrape the schedule and materials table into R from the course webpage (https://introdatasci.dlilab.com/schedule_materials/). Read the documentation of rvest so you get a better idea about the functions provided by rvest and their usages



```{r}
library(tidyverse)
library(rvest)
url_data <- "https://introdatasci.dlilab.com/schedule_materials/"
url_data %>% 
  read_html()
```
```{r}
css_selector <- "#main > table"
```
```{r}
x<- url_data %>% 
  read_html() %>% 
  html_element(css = css_selector) %>% 
  html_table()
x
```


## 2. With the extracted data frame, create two new columns based on the Date column: month and day. month would be the month abbrevations from the Date column; day would be the numeric numbers from the Date column. Although you can use whatever approach to get this done (do not enter them by hand…), I suggest you try to practice regular expression here (sub() or stringr::str_extract()).
```{r}
library(stringr)
x$day <- str_extract(x$Date, "\\d{2}") 
x$month <- str_extract(x$Date, "\\D{3}")
```


```{r}
x$day <- as.numeric(as.character(x$day))
x
```


## 3. With the data frame generated from Q2, use group_by() and summarise() to find out the number of lectures for each month, order the results by the number of lectures (high to low).

```{r}
y <- x %>% group_by(month) %>% summarise(lecture_number = n()) %>% arrange(desc(lecture_number))
y
```


## 4. For the Topic column, split all values into words (hint: stringr::str_split()). Observe the values in the Topic column and use regular expression to specify the pattern in the stringr::str_split() or strsplit() function. Once this is done, you should get a list of list, you can use unlist() to convert it into a vector and name it as words. Use table() and sort() to find the top 5 most frequent words.


```{r}
w <- strsplit(x$Topic, split = " ")
w
w1 <- unlist(w)
w1
```
```{r}
sort(table(w1),decreasing=TRUE)[1:5]
```




